---
title: "Getting started with OpenWeatherPull"
author: "Alex Hallam"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 3
vignette: >
  %\VignetteIndexEntry{Getting started with OpenWeatherPull}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
library(keyring)
knitr::opts_chunk$set(
  fig.width = 7,
  fig.height = 5,
  eval = !(keyring::key_get('openweather_map') == ""),
  cache = TRUE,
  collapse = TRUE,
  comment = "#>"
)
library(OpenWeatherPull)
options(digits = 4)
```

# Introduction

`OpenWeatherPull` provides a complete set of `R` bindings to the [Open Weather Map]
(https://openweathermap.org/) RESTful API. The following functions are available to
the users.

- `openweather_set_key("my_api_key")` - Set the required Open Weather Map API key for the session.
- `openweather()` - Fetch the weather data.
- `openweather_request()` - Send a general request to the Open Weather Map API.

Objects are returned as `tibbles`.

## Installation

```{r installation_github, eval=FALSE}
# install.packages("devtools")
devtools::install_github("alexhallam/OpenWeatherPull")
```

Load package

```{r fredr_load, eval=FALSE}
library(OpenWeatherPull)
```

## Authentication

To use `OpenWeatherPull`, you must first [obtain a Open Weather Pull API
key](https://openweathermap.org/api). Once you've obtained an API key, you 
can set the key as an environment variable using `openweather_set_key`.

```{r fredr_set_key, eval=FALSE}
openweather_set_key("abcdefghijklmnopqrstuvwxyz123456")
```

where "abcdefghijklmnopqrstuvwxyz123456" is replaced with the actual key you obtain from Open Weather Map. This will set the key for the current session. 

## Retrieve series observations
Example
-------

This is a basic example which shows you how to solve a common problem:

``` r
devtools::install_github("alexhallam/OpenWeatherPull")
openweather_set_key("my_api_key") # use API key provided by Open Weather Map
weather_data <- openweather(id = "5074472", type = "today", units = "i")
weather_data
```

If you have subscribed for the 16 day forecast API you may also run the following

``` r
openweather(id = "4560349", type = "forecast", cnt = 14, units = "i")
```

`OpenWeatherPull` plays nicely with tidyverse functions such as `pmap_dfr`:

Current Weather
---------------

``` r
library(tidyverse)
library(purrr)
# a sample set of cities for current weather data
id <- c("4560349","4464368","4180439","4188377","4861716","5263058",
            "4257227","4644585","4335045", "4887398","5037649","4850751",
            "4281730","4553433","5074472","4684888","5454711","5780993",
            "5506956","5391959","5308655","5809844","4393217","4544349","4699066","5344994")
type <- rep("today",length(cities))
cnt <- rep(14,length(cities)) # not used but error is thrown without it. Fix in next release
units <- rep("i",length(cities))
pmap_dfr(list(id, type, cnt, units), openweather) #all is clouds.all = Cloudiness, %
```

Forecast -- Requires paid API key
---------------------------------

``` r
# a sample set of cities for forecast data
type <- rep("forecast",length(cities))
cnt <- rep(14,length(cities))
units <- rep("i",length(cities))
pmap_dfr(list(id, type, cnt, units), openweather)
```


